manuscript_outline

### 2025-07-02 docs/manuscript/paper.Rmd
copy edits

| Class | Order | Genera | Species | Study |
|:--------------|:--------------|:--------------|:--------------|:--------------|
| Amphibia | Anura | *Lithobates* | *L. sylvaticus* | @moore1939 |
|  |  |  | *L. pipiens* |  |
|  |  |  | *L. clamitans* |  |
|  |  |  | *L. palustris* |  |
|  |  | *Ascaphus* | *A. truei* | @brown1975 |
|  | Urodela | *Ambystoma* | *A. gracile* | @brown1976 |
| Reptilia | Squamata | *Sceloporus* | *S. undulatus* | @angilletta2000 |
|  |  | *Podarcis* | *P. mural*is | @vandamme1992 |
|  | Testudines | *Mauremys* | M. reevesii | @du2007 |
|  |  |  | 181 species | 141 studies in @while2018 |
| Insecta | Plecoptera | *Nemurella* | *N. pictetii* | @brittain1978, @elliott1984 |
|  |  | *Capnia* | *C. atra* | @brittain1984 |
|  |  | *Capnia* | *C. bifrons* | @elliott1986 |
|  |  | *Mesocapnia* | *M. oenone* | @brittain1984 |
|  |  | *Taeniopteryx* | *T. nebulosa* | @brittain1977 |
|  | Coleoptera | *Colaphellus* | *C. bowringi* | @tang2017 |
|  |  |  | 18 species | Developmental equations in @pritchard1987 |
| Malacostraca | Decapoda | *Pontastacus* | *P. leptodactylus* | @aydin2004 |

>>>>

| Class        | Order      | Genera         | Species            | Study                                     |
|:-------------|:-----------|:---------------|:-------------------|:------------------------------------------|
| Amphibia     | Anura      | *Lithobates*   | *L. sylvaticus*    | @moore1939                                |
|              |            |                | *L. pipiens*       |                                           |
|              |            |                | *L. clamitans*     |                                           |
|              |            |                | *L. palustris*     |                                           |
|              |            | *Ascaphus*     | *A. truei*         | @brown1975                                |
|              | Urodela    | *Ambystoma*    | *A. gracile*       | @brown1976                                |
| Reptilia     | Squamata   | *Sceloporus*   | *S. undulatus*     | @angilletta2000                           |
|              |            | *Podarcis*     | *P. mural*is       | @vandamme1992                             |
|              | Testudines | *Mauremys*     | M. reevesii        | @du2007                                   |
|              |            |                | 181 species        | 141 studies in @while2018                 |
| Insecta      | Plecoptera | *Nemurella*    | *N. pictetii*      | @brittain1978, @elliott1984               |
|              |            | *Capnia*       | *C. atra*          | @brittain1984                             |
|              |            | *Capnia*       | *C. bifrons*       | @elliott1986                              |
|              |            | *Mesocapnia*   | *M. oenone*        | @brittain1984                             |
|              |            | *Taeniopteryx* | *T. nebulosa*      | @brittain1977                             |
|              | Coleoptera | *Colaphellus*  | *C. bowringi*      | @tang2017                                 |
|              |            |                | 18 species         | Developmental equations in @pritchard1987 |
| Malacostraca | Decapoda   | *Pontastacus*  | *P. leptodactylus* | @aydin2004                                |
